### 2020-12-27 latex/vnhcs.tex
Final edit of VNHC chapter for the lit review

>>>>

\section{Comparison with Existing VNHC Literature}\label{ch:vnhc-compare}

Griffin and Grizzle were the first to define relative degree \(\{2,\ldots,2\}\)
VNHCs (see \cite{nhvc_dynamic_walking} and \cite{nhvc_gait_optimization}). 
They required that the first coordinate be unactuated, so 
\citet{hybrid_zero_dynamics_bipedal_nhvcs} extended their work to more general
mechanical systems by defining the unactuated coordinate \(q_u = B^\perp q\).
These ideas are what inspired us to use simply actuated Hamiltonian systems,
which are more suitable for the study of VNHCs than Lagrangian mechanics.

Our definition of a VNHC is more general than that of Griffin and
Grizzle.
They define a VNHC as a relation \(h(q,\sigma_u)\), where \(\sigma_u\) is the
Lagrangian mechanics proxy for \(p_u\).
Their definition carries an implicit assumption that VNHCs are of
relative degree \(\{2,\ldots,2\}\), which are what we call regular VNHCs.
By contrast, our definition of a VNHC allows for relations \(h(q,p)\)
that use the full phase.
We are the first to distinguish these from regular VNHCs, and to
provide the characterization of regularity in Theorem \ref{thm:vnhc-regularity}.

\citet{hybrid_zero_dynamics_bipedal_nhvcs} derive the
constrained dynamics for VNHCs of the form \(h(q,\sigma_u)\).
Our derivation of the constrained dynamics in Theorem
\ref{thm:zero-dynamics} uses the same assumptions they require, with the
additional assumption that one can solve for \(q_a = f(q_u,p_u)\) on the
constraint manifold.
While this means Horn \etal's constrained dynamics hold for a larger class of
VNHCs, their derivations are obscured by a complicated change of coordinates
when finding the closed form of the dynamics. 
By making the aforementioned additional assumption, we are instead able to find
the constrained dynamics in terms of the unactuated coordinates.
This makes our constrained dynamics more physically intuitive, since they
describe the behaviour of a specific part of the mechanical system.
This additional structure will facilitate our analysis of the energy injection
properties of VNHCs across the next two chapters.
